Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2018-02-15 paperIEEE.tex
Tweaks
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@134 db7c848b-7755-4df2-b763-8796797afa52
First submission
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@135 db7c848b-7755-4df2-b763-8796797afa52

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
  \begin{abstract}
    Developing complex, real world graphics applications which leverage multiple
    GPUs and computers for interactive 3D rendering tasks is a complex task. It
    requires expertise in distributed systems and parallel rendering in addition
    to the application domain itself. We present a mature parallel rendering
    framework which provides a large set of features, algorithms and system
    integration for a wide range of real-world research and industry
    applications. Based on the basic architecture and implementation of the
    \textsf{Equalizer} parallel rendering framework presented in \cite{EMP:09},
    we show how a variety of generic algorithms can be integrated in the framework
    to help application scalability and development in many different domains,
    highlighting how concrete applications benefit from the diverse aspects and use
    cases of \textsf{Equalizer}, and we present new experimental results for parallel
    rendering and data distribution.
  \end{abstract}

@@

\begin{figure*}[ht]%
\includegraphics[height=.17\textwidth]{images/benchmark_eVolve}\hfil
\includegraphics[height=.17\textwidth]{images/benchmark_eqPly2}\hfil
\includegraphics[height=.17\textwidth]{images/spikes512}\hspace{.5mm}\includegraphics[height=.17\textwidth]{images/beechnut}
  \caption{\label{fBenchmarks}Benchmark data: Flower alley with 30 volume models
  of $1024^3$ unsigned bytes (1\,GB) each (left); David alley with 30 statues of
  56\,M triangles (988\,MB) each (middle); Volumes used for object distribution
  benchmarks (right): spike frequencies of a three million neuron electrical
  simulation at $512\times437\times240$ unsigned byte (51\,MB) and an MicroCT scan of a
  beechnut at $1024\times1024\times1546$ unsigned short (3\,GB) resolution}
\end{figure*}

>>>>

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
  \begin{abstract}
    Developing complex, real world graphics applications which leverage multiple
    GPUs and computers for interactive 3D rendering tasks is a complex task. It
    requires expertise in distributed systems and parallel rendering in addition
    to the application domain itself. We present a mature parallel rendering
    framework which provides a large set of features, algorithms and system
    integration for a wide range of real-world research and industry
    applications. Using the \textsf{Equalizer} parallel rendering framework, we
    show how a wide set of generic algorithms can be integrated in the framework
    to help application scalability and development in many different domains,
    highlighting how concrete applications benefit from the diverse aspects and
    use cases of \textsf{Equalizer}. We present novel parallel rendering
    algorithms, powerful abstractions for large visualization setups and virtual
    reality, as well as new experimental results for parallel rendering and data
    distribution.
  \end{abstract}

@@

\begin{figure*}[ht]%
\includegraphics[height=.17\textwidth]{images/benchmark_eVolve}\hfil
\includegraphics[height=.17\textwidth]{images/benchmark_eqPly2}\hfil
\includegraphics[height=.17\textwidth]{images/spikes512}\hspace{.2mm}\includegraphics[height=.17\textwidth]{images/beechnut}
  \caption{\label{fBenchmarks}Benchmark data: Flower alley with 30 volume models
  of $1024^3$ unsigned bytes (1\,GB) each (left); David alley with 30 statues of
  56\,M triangles (988\,MB) each (middle); Volumes used for object distribution
  benchmarks (right): spike frequencies of a three million neuron electrical
  simulation at $512\times437\times240$ unsigned byte (51\,MB) and an MicroCT scan of a
  beechnut at $1024\times1024\times1546$ unsigned short (3\,GB) resolution}
\end{figure*}
